% Extracted from main.tex — consider converting to BibTeX (.bib)
\begin{thebibliography}{99}

\bibitem{beran2013}
Beran, T. N., et al. (2013). The effect of a humanoid robot on reducing anxiety in pediatric patients undergoing medical procedures. \textit{Journal of Health Psychology}, 18(7), 931-941.


\bibitem{garingo2016}
Garingo, A., et al. (2016). The use of telestroke in the management of acute ischemic stroke. \textit{The Neurologist}, 21(2), 21-25.

\bibitem{kristoffersson2013}
Kristoffersson, A., Coradeschi, S., \& Loutfi, A. (2013). A review of mobile robotic telepresence. \textit{Advances in Human-Computer Interaction}, 2013, 1-17.

\bibitem{laranjo2018}
Laranjo, L., et al. (2018). Conversational agents in healthcare: a systematic review. \textit{Journal of the American Medical Informatics Association}, 25(9), 1248-1258.

\bibitem{alshishtawy2013}
Al-Shishtawy, A., \& Al-Khanjari, Z. (2013). Telemedicine requirements for treatment network in Oman. \textit{2013 International Conference on Computing, Electrical and Electronic Engineering (ICCEEE)}, 465-470.

\bibitem{alsalmani2023}
Al-Salmani, M. A., et al. (2023). Usability of telephone-based telemedicine in primary healthcare in Oman during COVID-19 pandemic. \textit{BMC Health Services Research}, 23(1), 1-11.

\bibitem{alsheikhly2006}
Al-Sheikhly, D., et al. (2006). Four decades of progress: Evolution of the health system in Oman. \textit{Sultan Qaboos University Medical Journal}, 6(1), 9-22. PMC3074664.

\bibitem{alhinai2024}
Al-Hinai, H., et al. (2024). Health system performance assessment and reforms, Oman. \textit{Bulletin of the World Health Organization}, 102(6), 428-435. PMC11197650.

\bibitem{ollikkala2020}
Ollikkala, M., et al. (2020). Autonomous mobile robots in hospital environments: A systematic literature review. \textit{Journal of Healthcare Engineering}, 2020.

\bibitem{sabanovic2013}
Šabanović, S., et al. (2013). Robots in practice: A situated analysis of meaning-making in human-robot interaction. \textit{Proceedings of the 8th ACM/IEEE International Conference on Human-Robot Interaction}, 333-340.

\bibitem{broekens2009}
Broekens, J., Heerink, M., \& Rosendal, H. (2009). Assistive social robots in elderly care: A review. \textit{Gerontechnology}, 8(2), 94-103.

\bibitem{imarc2024}
IMARC Group. (2024). Robotic vacuum cleaner market size to hit USD 31.79 billion by 2033. \textit{Market Research Report}.

\bibitem{scmp2024}
South China Morning Post. (2024). Roomba revolution: How China swallowed up the robot vacuum market. \textit{SCMP Economy}.

\bibitem{neato2025}
Consegic Business Intelligence. (2025). Residential robotic vacuum cleaner market size, report, trend analysis 2032. \textit{Market Analysis}.

\bibitem{trendforce2024}
TrendForce. (2024). Global service robot sales analysis. \textit{Industry Report}.

\bibitem{taranta2021}
Taranta, D., Marques, F., Lourenço, A., Prates, P. A., et al. (2021). An Autonomous Mobile Robot Navigation Architecture for Dynamic Intralogistics. In \textit{Proceedings - 2021 IEEE 19th International Conference on Industrial Informatics (INDIN)}.



\bibitem{amazon2025}
Amazon. (2025). Amazon deploys over 1 million robots and launches new AI. \textit{About Amazon News}.

\bibitem{robotsguide2023}
Robots Guide. (2023). Proteus - Your guide to the world of robotics. \textit{Robotics Database}.

\bibitem{amazon2022}
Amazon Science. (2022). Amazon's tiny robot drives do the heavy lifting. \textit{Amazon Science News}.

\bibitem{agv2024}
AGV Network. (2024). Amazon warehouse robots. \textit{AGV Industry Resources}.

\bibitem{amazon2024ai}
Amazon. (2024). Amazon has more than 750,000 robots that sort, lift, and carry packages. \textit{About Amazon Operations}.

\bibitem{intel2024}
Intel Corporation. (2024). Robotics in healthcare: The future of robots in medicine. \textit{Intel Learn Resources}.

\bibitem{frontiers2024}
Frontiers. (2024). Advancing healthcare through mobile collaboration: A survey of intelligent nursing robots research. \textit{Frontiers in Public Health}.

\bibitem{pmc2024nursing}
PMC. (2024). Advancing healthcare through mobile collaboration: A survey of intelligent nursing robots research. \textit{PubMed Central}, PMC11628269.

\bibitem{sciencedirect2021}
ScienceDirect. (2021). Intelligent disinfection robots assist medical institutions in controlling environmental surface disinfection. \textit{Intelligent Medicine}, 1(2), 88-93.

\bibitem{mdpi2024}
MDPI. (2024). Robotics applications in the hospital domain: A literature review. \textit{Robotics}, 7(6), 125.

\bibitem{ahu2024}
AdventHealth University. (2024). Robotics in healthcare: Past, present, and future. \textit{AHU Blog}.

\bibitem{jmir2024}
Journal of Medical Internet Research. (2024). Advances in the application of AI robots in critical care: Scoping review. \textit{JMIR}, 2024(1), e54095.

\bibitem{li2022}
Li, Z., Wang, J., Li, X., Tan, M., \& Wang, W. (2022). An Autonomous Mobile Robot Navigation System for Dynamic Environments Based on an Improved Timed-Elastic-Band Local Planner. \textit{Electronics}, 11(20), 3294.

\bibitem{weinmann2023}
Weinmann, K., \& Simske, S. (2023). Design of Bluetooth 5.1 Angle of Arrival Homing Controller for Autonomous Mobile Robot. \textit{Robotics}, 12(4), 115.

\bibitem{doduc2024}
Do Duc, M., Nguyen Canh, T., DoNgoc, M., \& HoangVan, X. (2024). Fusion LiDAR-Inertial-Encoder data for High-Accuracy SLAM. \textit{arXiv preprint arXiv:2407.11870}.

\bibitem{tourani2022}
Tourani, A., Bavle, H., Sanchez-Lopez, J. L., \& Voos, H. (2022). Visual SLAM: What Are the Current Trends and What to Expect?. \textit{Sensors}, 22(23), 9297.

\bibitem{musick2025}
Musick, E. (2025). A Comparative Analysis of Leading Large Language Models (LLMs) in Early 2025. \textit{Medium}.

\bibitem{civo2024}
Civo. (2024). Open Source vs. Proprietary LLMs. \textit{Civo Blog}.

\bibitem{irobot2024create3}
iRobot Corporation. (2024). iRobot Create 3: Educational Robot Platform. Retrieved from \texttt{https://edu.irobot.com/create3}

\bibitem{slamtec2024}
SLAMTEC Co., Ltd. (2024). SLAMTEC Apollo Autonomous Mobile Robot Development Platform. Retrieved from \texttt{https://www.slamtec.com}

\bibitem{turtlebot2024}
Open Robotics. (2024). TurtleBot 4: The Next Generation Robot for Education and Research. Retrieved from \texttt{https://turtlebot.github.io}

\bibitem{yahboom2024}
Yahboom Technology. (2024). ROSMASTER X3 ROS Robot Car with Mecanum Wheels. Retrieved from \texttt{https://www.yahboom.net}

\bibitem{elephantrobotics2024}
Elephant Robotics. (2024). myAGV 2023: Autonomous Mobile Robot Platform. Retrieved from \texttt{https://www.elephantrobotics.com}

\bibitem{agilex2024}
AgileX Robotics. (2024). LIMO Pro: Multi-Modal Mobile Robot Platform. Retrieved from \texttt{https://www.agilex.ai}

\bibitem{husarion2024}
Husarion. (2024). ROSbot 2R: Autonomous Mobile Robot for ROS Developers. Retrieved from \texttt{https://husarion.com}

\end{thebibliography}